---
title: "{{TITLE}}"
subtitle: "Scanpath strategy report scaffold"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
format:
  html:
    toc: true
    toc-title: "Contents"
    toc-depth: 3
    toc-location: right
    number-sections: true
    number-depth: 3
    theme:
      light: cosmo
      dark: darkly
    respect-user-color-scheme: true
    embed-resources: true
    smooth-scroll: true
    anchor-sections: true
    code-fold: true
    code-summary: "Show R code"
    df-print: paged
    link-external-icon: true
    css: report-style.css
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

```{r setup}
#| cache: false
suppressPackageStartupMessages({
  library(dplyr)
  library(housereportstyle)
  library(ggplot2)
  library(readr)
  library(tibble)
})

set.seed(1001)

report_id <- "{{REPORT_ID}}"
output_dir <- file.path("generated")
plot_dir <- file.path(output_dir, "plots")
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)
```

## Scope

State which experiment, reconstruction layer, and participant-trial universe this report uses. Keep source-condition provenance visible before collapsing or modelling.

## Scanpath Representation

Use reconstructed behavioural events or gaze fixations to build participant-trial scanpaths. Consecutive duplicate locations should be removed when the analysis is about transitions; later revisits should be retained.

```{r scanpath_inputs_model}
#| cache: true
# Replace these placeholders with validated event and trial-metric tables.
scanpath_manifest <- tibble(
  metric = c("analysis_id", "duration_normalization", "mds_dimension_candidates"),
  value = c(report_id, "durations", "2, 3, 4, 5, 6, 7, 8, 9, 10")
)
```

```{r tbl-scanpath-manifest}
#| tbl-cap: "*Scanpath representation manifest*"
#| dependson: scanpath_inputs_model
reader_table(
  scanpath_manifest,
  note = "The manifest records preprocessing and ScaSim settings before clustering."
)
```

@tbl-scanpath-manifest should let the reader see exactly what is being treated
as a scanpath.

## MDS And Clustering

Fit lower-dimensional maps over 2-10 dimensions, record `isoMDS` stress, fit `Mclust` over the report-specified cluster-count range, and choose the final map using the stated rule.

```{r mds_dimension_sweep_model}
#| cache: true
# In a real report, call fit_scanpath_dimension_sweep() after compute_scasim_distance().
mds_dimension_sweep <- tibble(
  mds_dimensions = 2:10,
  stress = c(30, 22, 17, 14, 12, 10.5, 9.5, 8.8, 8.2),
  selected_clusters = c(5, 6, 8, 8, 9, 10, 10, 9, 8),
  model_name = "example",
  bic = NA_real_,
  mean_uncertainty = NA_real_,
  smallest_cluster = NA_real_,
  largest_cluster = NA_real_,
  status = "ok",
  message = ""
)

mds_selection <- select_scanpath_mds_dimension(mds_dimension_sweep)
dimension_sweep <- list(summary = mds_dimension_sweep, selection = mds_selection)
```

```{r fig-mds-dimension-selection}
#| fig-width: 8.5
#| fig-height: 5.2
#| out-width: "100%"
#| fig-cap: "*MDS dimensionality selection*"
#| fig-cap-location: top
#| dependson: mds_dimension_sweep_model
mds_dimension_plot <- plot_mds_dimension_selection(dimension_sweep)

save_report_plot(mds_dimension_plot, "mds-dimension-selection.png", plot_dir, width = 8.5, height = 5.2)
mds_dimension_plot
```

::: {.aside}
_Note._ Candidate maps use ScaSim dissimilarities, `isoMDS` stress, and `Mclust` BIC-selected cluster counts. Horizontal reference lines mark stress values of 5 and 10; the vertical guide marks the selected dimensionality.
:::

@fig-mds-dimension-selection is the required diagnostic before interpreting cluster assignments.

## Hidden Checks

```{r internal_validation_checks}
#| include: false
#| cache: true
#| dependson:
#|   - mds_dimension_sweep_model
acceptance_checks <- tibble(
  check = c("dimension sweep covers 2-10", "selected dimension is valid"),
  passed = c(
    setequal(mds_dimension_sweep$mds_dimensions, 2:10),
    mds_selection$selected_mds_dimensions[[1]] %in% 2:10
  )
)

write_csv(acceptance_checks, file.path(output_dir, "acceptance_checks.csv"))
```
