---
title: "{{TITLE}}"
date: last-modified
date-format: "YYYY-MM-DD HH:mm:ss"
format:
  html:
    toc: true
    toc-title: "Contents"
    toc-depth: 3
    toc-location: left
    number-sections: true
    number-depth: 3
    theme:
      light: cosmo
      dark: darkly
    respect-user-color-scheme: true
    embed-resources: true
    smooth-scroll: true
    anchor-sections: true
    code-fold: true
    code-summary: "Show R code"
    df-print: paged
    link-external-icon: true
    css: report-style.css
execute:
  echo: false
  warning: false
  message: false
  cache: true
---

```{r setup}
#| cache: false
suppressPackageStartupMessages({
  library(dplyr)
  library(housereportstyle)
  library(ggplot2)
  library(readr)
  library(tibble)
})

set.seed(1001)

report_id <- "{{REPORT_ID}}"
output_dir <- file.path("generated")
plot_dir <- file.path(output_dir, "plots")
dir.create(plot_dir, recursive = TRUE, showWarnings = FALSE)
```

## Scope

State the analysis boundary, data source, and the scientific question in plain prose.

## Data Inputs

```{r data_inputs_model}
#| cache: true
example_data <- tibble(
  group = rep(c("condition_a", "condition_b"), each = 5),
  trial = rep(1:5, times = 2),
  value = c(4, 5, 6, 6, 7, 3, 4, 4, 5, 6)
)
```

```{r data_input_table}
#| dependson: data_inputs_model
reader_table(
  example_data,
  label = "Table 1",
  title = "Example data scaffold",
  note = "Replace this scaffold table with the first reader-facing data provenance table."
)
```

Table 1 should explain what the reader needs to know before the first plot or model.

```{r fig-example-summary}
#| fig-width: 7
#| fig-height: 4.5
#| out-width: "100%"
#| fig-cap: "*Example grouped summary*"
#| fig-cap-location: top
#| dependson: data_inputs_model
example_plot <- example_data |>
  ggplot(aes(x = trial, y = value, colour = group)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  labs(x = "Trial", y = "Value", colour = "Group") +
  theme_report(base_size = 11)

save_report_plot(example_plot, "example-summary.png", plot_dir, width = 7, height = 4.5)
example_plot
```

::: {.aside}
_Note._ Replace this aside with a figure note that explains how to read the plot; keep titles and numbering in Quarto.
:::

@fig-example-summary demonstrates the report's figure grammar: Quarto caption above, image next, note in a margin aside, then interpretive prose.

## Hidden Checks

```{r internal_validation_checks}
#| include: false
#| cache: true
#| dependson:
#|   - data_inputs_model
acceptance_checks <- tibble(
  check = "example input contains rows",
  passed = nrow(example_data) > 0
)

write_csv(acceptance_checks, file.path(output_dir, "acceptance_checks.csv"))
```
